Synthesis of Linear Functional Programs

### 2021-07-16 article/article.tex
minor intro tweaks

In this paper we present a framework for synthesis of linear types extended with
recursive algebraic data types, parametric polymorphism and refinements.
% TODO: extensible? proving feasability of... ? showing potential for ... ?

First, we discuss the use of linear types as specifications, the outline of the
synthesis process, and what that entails for the synthetiser -- ilustrated with
concrete results (Section~\ref{sec:overview}). Then, we present the
algorithm and formal system driving the synthesis
(Section~\ref{sec:formal_system}). Aftwerwards, we describe the architecture 
of our synthetiser named \synname, and examine technical details and challenges of the
implementation (Section~\ref{sec:architecture}). Finally, we evaluate our work
through expressiveness benchmarks (i.e.~can we synth $X$?) and time benchmarks
(i.e.~how fast can we synth a term of type $T$?) (Section~\ref{sec:evaluation}).
%TODO: And appendice with...

>>>>

\paragraph{Contributions}
In this paper we present a framework for synthesis of linear types extended with
recursive algebraic data types, parametric polymorphism and refinements.
% TODO: extensible? proving feasability of... ? showing potential for ... ?

\paragraph{Outline}
First, we discuss the use of linear types as specifications, the outline of the
synthesis process, and what that entails for the synthetiser -- ilustrated with
concrete results (Section~\ref{sec:overview}). Then, we present the
algorithm and formal system driving the synthesis
(Section~\ref{sec:formal_system}). Aftwerwards, we describe the architecture 
of our synthetiser named \synname, and examine technical details and challenges of the
implementation (Section~\ref{sec:architecture}). Finally, we evaluate our work
through expressiveness benchmarks (i.e.~can we synth $X$?) and time benchmarks
(i.e.~how fast can we synth a term of type $T$?) (Section~\ref{sec:evaluation}).
%TODO: And appendice with...
